Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers

### 2023-10-27 paper/paper.tex
paper: Add "case study" to title
paper: Explain what is "not scalable" to traditional approaches

\title{Improving reproducibility of scientific software using Nix/NixOS}

@@

In scientific research, it's crucial to be able to reproduce and verify results.
Reproducibility ensures that experiments can be repeated and findings can be validated, which is essential for reliable and credible research.
Being able to replicate experiments and computations is important for verifying scientific claims.
However, achieving reproducibility in scientific software has been a challenge due to complex dependencies, conflicting software environments, and changing software systems.
Problems arise from dependencies, library versions, and system configurations, leading to inconsistencies across different computing environments.
Traditional approaches to reproducibility, such as manual setup instructions or virtualization techniques, are time-consuming, prone to errors, and not scalable.
This calls for a more efficient and automated solution.

>>>>

\title{Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers}

@@

In scientific research, it's crucial to be able to reproduce and verify results.
Reproducibility ensures that experiments can be repeated and findings can be validated, which is essential for reliable and credible research.
Being able to replicate experiments and computations is important for verifying scientific claims.
However, achieving reproducibility in scientific software has been a challenge due to complex dependencies, conflicting software environments, and changing software systems.
Problems arise from dependencies, library versions, and system configurations, leading to inconsistencies across different computing environments.
Traditional approaches to reproducibility, such as manual setup instructions or virtualization techniques, are time-consuming, and prone to errors.
It is not scalable and inefficient to make every researcher to tediously recreate the exact same environment with traditional approaches.
This calls for a more efficient and automated solution.
